What should I notice? Evaluating the memorability of events for abductive inference.

### 2021-10-14 new_paper.tex
switching to MDPI template

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{url}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage[ruled,linesnumbered]{algorithm2e}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\title{
What should I notice? Evaluating the memorability of events for abductive inference.
}
\author{
  \IEEEauthorblockN{
\IEEEauthorrefmark{1}\IEEEauthorrefmark{2} Étienne Houzé,
\IEEEauthorrefmark{1} Jean-Louis Dessalles,
\IEEEauthorrefmark{1} Ada Diaconescu,
\IEEEauthorrefmark{2} David Menga
  }

  \IEEEauthorblockA{\IEEEauthorrefmark{1}
    Télécom Paris, IP Paris, \emph{Palaiseau}, France\\
email: \{first\}.\{second\}@telecom-paris.fr}
  \IEEEauthorblockA{\IEEEauthorrefmark{2} EDF R\&{}D, \emph{Palaiseau}, France\\
email: \{first\}.\{second\}@edf.fr}
}

\maketitle

\begin{abstract}
  When confronted to an unprecedented situation, humans typically show good
  performance in quickly identifying noticeable past events and proposing them
  as possible causal hypotheses. This kind of abductive inference is widely
  overlooked in modern AI approaches which rely on massive datasets to learn
  associative patterns. Our proposal is to formalize and compute a ``memorability''
score over a set of events recorded from a cyber-physical system.
This score can then be used to select relevant information to be
remembered and to propose causal hypotheses in unusual situations on demand.
The approach is meant to be complementary to more traditional
learning-focused abduction techniques. We provide theoretical ground for our approach
based on Algorithmic Information
Theory. We also provide an implementation example, a
smart-home scenario, to show how our approach could translate in practice.
\end{abstract}

\begin{IEEEkeywords}
Kolmogorov complexity, Algorithmic Information Theory, Simplicity, Abduction, Surprise
\end{IEEEkeywords}

@@

% As the number of connected devices and sensors grows, so does the amount of
% produced data. As a consequence, the ability to filter out a few events from past recordings
% as ``memorable'' becomes prime. While this task is often overlooked by many
% statistical approaches, which instead benefit from large quantity of
% information, it is part of the learning process for humans
% \cite{dehaene_how_2020}. Faced with new situations, humans are prone to infer
% previously seen unusual events as possible causes, and carry out further testing
% to assess the existence of a causal relation.

@@

\section{Theoretical Background}
\label{sec:theory}
Kolmogorov complexity formally quantifies the amount of information required
for the computation of a finite binary string\footnote{Though the definition
holds for some infinite binary strings (think of the representation of the
decimals of $\pi$), we restrict ourselves here to finite strings.} (or
any object represented by a finite binary
string)\cite{kolmogorov_three_1965,li_introduction_2008}. The complexity $K(s)$ of a (finite) binary string is the length in bits of the shortest program $p$
which, if given as input to a universal Turing Machine $U$, outputs $s$.
\begin{equation}
  \label{eq:kolmo_def}
  K_{U}(s) = \min_{p}\left\{l(p)|U(p)=s\right\}
\end{equation}

@@

\section{Computing the memorability of events}
\label{sec:computing}
\subsection{Retrieving an event}

@@

To model how humans are able to describe events by using qualifiers, we use \emph{predicates}: Boolean functions operating on events and, possibly, additional parameters: $\pi(e, a_1, a_2, \dots, a_n) \mapsto \{O,1\}$ is a predicate of arity $n$ operating on event $e$. In the rest of this paper, we will prefer the equivalent notation $\pi(e, k) \mapsto \{0,1\}$, where $k$ is a binary string encoding the sequence of arguments $a_1, \dots, a_n$. Using this notation, the predicate $\pi$ becomes a boolean function operating on $\mathbf{E} \times \{0,1\}^*$:
\begin{equation}
  \label{eq:predicate}
  \pi : \begin{cases}
\mathcal{M}\times \{0,1\}^{*} &\mapsto \{0,1\} \\
(e, k) &\mapsto \pi_{k}(e)
\end{cases}
\end{equation}
As an example of predicate, consider $\pi = \mathtt{year}$ and $k$ a string encoding the number $1$, thus
constructing the predicate $\mathtt{year(}e, 1\mathtt{)}$, which tells whether
the event $e$ occurred $1$ year ago.

@@

\subsection{Description complexity of events}

@@

\subsection{Computing Memorability}
As stated in Equation \ref{eq:memorability}, we define memorability $M(e)$ as the absolute difference between the description complexity of an event and its expected value. As we've just defined $K_d(e)$ and provided an approximation in Equation \ref{eq:approx_k_desc}, we now focus on defining the \emph{expected} description complexity of an event, $K_{exp}(e)$ that appears in Equation \ref{eq:memorability}

@@

\subsection{From memorability to abduction}
% On peut étendre la définition utilisée pour la surprise en faisant intervenir
% les prédicats'' `sympathiques` par rapport à ce que l'on questionne.
Abductive inference builds on the computation
of the memorability score. \emph{Knowing} that we want to find a cause $c$
for an observed effect $e$, we try to find the most remarkable event in past
memory that is related to $e$. While our ``memorability'' score identifies remarkable past events, it does not take into account their relatedness to $e$.

@@

\section{Implementation Example}
\label{sec:example}
\subsection{Setup}
We considere here an experimental smart home setup. This choice of
configuration is motivated by the challenges posed by smart homes for abductive
inference: i) as the number of connected devices increases, more events are
recorded, making the detection of memorable events more important; ii) smart
homes are prone to experience atypical situations, highly dependent on the context,
for which pre-established relations might fail to find good abduction
candidates. Our choice was also motivated by
the existence of previous work involving smart home simulations capable of quickly generating data from which we could extract events and test our methods.

% In order to provide an acceptable setup to our experiments, we used the scenario
% of smart homes. This kind of scenario is a prime example of situations where
% innovative methods of abduction can prove useful, for various reasons: i) as the
% number of sensors grows with the number of equipped devices in the house, not
% all recorded events are useful and should be remembered over long period of
% time; ii) atypical situations, which are the ones where abduction is most likely
% to be used (to explain situations to the user, or to solve a conflict), are also
% where the lack of past data makes knowledge acquisition hard.

To carry out the simulation, we built custom modules into the existing iCasa
smart home simulator\cite{lalanda_self-aware_2017}. ICasa
offers a simulation of autonomic systems that can handle internal communications,
the possible insertion of new components at runtime, or the deletion or modification of existing
components. We used a basic scenario consisting of a house with four rooms,
a single user, and an outdoor zone. All four rooms are equipped
with a temperature controller system that monitors and controls heaters (fig.
\ref{fig:view}).

@@

\subsection{Results}

\subsubsection{Memorability}

@@

The ``memorability score'' is shown in fig. \ref{fig:result1}.
% highlights these aforementioned events from the main ``usual'' sequence. Since
the computation of this measure treats unusually complex or unusually simple events the
same way (from the absolute value operation in Equation \ref{eq:unexpected}), we
observe that some events are memorable due to their context only. For instance,
a temperature anomaly occurring simultaneously to many other anomalies is
noticeable, as it is costlier than expected to distinguish it from its neighbors.

@@

Given that we generated the data used for this experiment, it is possible to
flag all perturbation events from the usual daily events and evaluate how a
detection based on ``memorability'' score would perform in distinguishing these
events. The result is presented as a ROC curve in fig. \ref{fig:roc}.

\textbf{TOOD:} Il faudrait commenter la courbe
\begin{figure}[ht]
  \centering
  \includegraphics[width=\linewidth]{./figures/roc}
  \caption{Experimental ROC curve (True Positive Rate against False Positive
Rate) for a classifier based on our memorability score. Measures consider 23
manually flagged events as memorable (events added to the normal background
as described in Section~\ref{sec:example}.)}
  \label{fig:roc}
\end{figure}
\subsubsection{Abduction}

@@

\subsubsection{Discussion}
\label{ssub:discussion}

\section{Related Works}
\label{sec:related}
\textbf{TODO: this section is still WIP: I've added most references and short comments, but I still need to write the story linking them.}
Our work is intended to be integrated into larger-scale frameworks to monitor
and detect events in complex environment such as smart homes. In these works, the
approach to smart homes is often regarded as self-organizing systems \cite{kramer_rigorous_2009,kounev_notion_2017}. As such, they present capacities of adaptation to new goals,
new components, new environment. A commonly used approach is the principle of
autonomic system, which minimizes user's intervention for management of the
system \cite{kounev_notion_2017,kephart_vision_2003}.

@@

\section{Perspectives}
\label{sec:future}
The main purpose of the present paper is to show the possible connections
between existing definitions of simplicity from cognitive science, Algorithmic
Information Theory and a practical use case in cyber-physical systems. As such,
many further improvements can be done to pave the way towards a better
integration and performance for anomaly detection or abduction.

@@

\section{Conclusion}

\bibliographystyle{IEEEtran}
\bibliography{biblio.bib}

\end{document}

>>>>

%  LaTeX support: latex@mdpi.com 
%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.

%=================================================================
\documentclass[entropy,article,submit,moreauthors,pdftex]{Definitions/mdpi}

% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept". The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}. This is especially recommended for submission to arXiv, where line numbers should be removed before posting. For preprints.org, the editorial staff will make this change immediately prior to posting.

%--------------------
% Class Options:
%--------------------
%----------
% journal
%----------
% Choose between the following MDPI journals:
% acoustics, actuators, addictions, admsci, adolescents, aerospace, agriculture, agriengineering, agronomy, ai, algorithms, allergies, analytica, animals, antibiotics, antibodies, antioxidants, appliedchem, applmech, applmicrobiol, applnano, applsci, arts, asi, atmosphere, atoms, audiolres, automation, axioms, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomechanics, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, brainsci, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coatings, colloids, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, crops, cryptography, crystals, curroncol, cyber, dairy, data, dentistry, dermato, dermatopathology, designs, diabetology, diagnostics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, entropy, environments, environsciproc, epidemiologia, epigenomes, fermentation, fibers, fire, fishes, fluids, foods, forecasting, forensicsci, forests, fractalfract, fuels, futureinternet, futuretransp, futurepharmacol, futurephys, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, hazardousmatters, healthcare, hearts, hemato, heritage, highthroughput, histories, horticulturae, humanities, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijtm, ijtpp, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jcdd, jcm, jcp, jcs, jdb, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jzbg, kidney, land, languages, laws, life, liquids, literature, livers, logistics, lubricants, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, metabolites, metals, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, minerals, mining, modelling, molbank, molecules, mps, mti, nanoenergyadv, nanomanufacturing, nanomaterials, ncrna, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, nri, nursrep, nutrients, obesities, oceans, ohbm, onco, oncopathology, optics, oral, organics, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacy, philosophies, photochem, photonics, physchem, physics, physiolsci, plants, plasma, pollutants, polymers, polysaccharides, proceedings, processes, prosthesis, proteomes, psych, psychiatryint, publications, quantumrep, quaternary, qubs, radiation, reactions, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, risks, robotics, safety, sci, scipharm, sensors, separations, sexes, signals, sinusitis, smartcities, sna, societies, socsci, soilsystems, solids, sports, standards, stats, stresses, surfaces, surgeries, suschem, sustainability, symmetry, systems, taxonomy, technologies, telecom, textiles, thermo, tourismhosp, toxics, toxins, transplantology, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, vetsci, vibration, viruses, vision, water, wevj, women, world

%---------
% article
%---------
% The default type of manuscript is "article", but can be replaced by: 
% abstract, addendum, article, book, bookreview, briefreport, casereport, comment, commentary, communication, conferenceproceedings, correction, conferencereport, entry, expressionofconcern, extendedabstract, datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, studyprotocol, systematicreview, supfile, technicalnote, viewpoint, guidelines, registeredreport, tutorial
% supfile = supplementary materials

%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.

%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.

%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.

%=================================================================
% MDPI internal commands
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
%\doinum{}
\pubyear{2021}
\copyrightyear{2021}
%\externaleditor{Academic Editor: Firstname Lastname} % For journal Automation, please change Academic Editor to "Communicated by"
\datereceived{} 
\dateaccepted{} 
\datepublished{} 
\hreflink{https://doi.org/} % If needed use \linebreak
%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, changepage, paracol, attrib, upgreek, cleveref, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption
\usepackage{algorithm2e}

%=================================================================
%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
\Title{What should I notice? Evaluating the memorability of events for abductive inference.
}

% MDPI internal command: Title for citation in the left column
\TitleCitation{What should I notice?}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0000-0000-000X} % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{Étienne Houzé $^{1,2}$*, Jean-Louis Dessalles $^{2}$, Ada Diaconescu$^{2}$ and David Menga $^{2}$}

% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{Firstname Lastname, Firstname Lastname and Firstname Lastname}

% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{Lastname, F.; Lastname, F.; Lastname, F.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad EDF R\&D ; \{first\}.\{last\}@edf.fr;
7 boulevard Gaspard Monge, 91120 Palaiseau, France\\
$^{2}$ \quad Télécom Paris; \{first\}.\{last\}@telecom-paris.fr;
19 place Marguerite Perey, 91120 Palaiseau, France}

% Contact information of the corresponding author
\corres{Correspondence: etienne.houze@telecom-paris.fr}

% Current address and/or shared authorship
% \firstnote{Current address: Affiliation 3} 
% \secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

%\simplesumm{} % Simple summary

%\conference{} % An extended version of a conference paper

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{ When confronted to an unprecedented situation, humans typically show good
performance in quickly identifying noticeable past events and proposing them
as possible causal hypotheses. This kind of abductive inference is widely
overlooked in modern AI approaches which rely on massive datasets to learn
associative patterns. Our proposal is to formalize and compute a ``memorability''
score over a set of events recorded from a cyber-physical system.
This score can then be used to select relevant information to be
remembered and to propose causal hypotheses in unusual situations on demand.
The approach is meant to be complementary to more traditional
learning-focused abduction techniques. We provide theoretical ground for our approach
based on Algorithmic Information
Theory. We also provide an implementation example, a
smart-home scenario, to show how our approach could translate in practice.}

% Keywords
\keyword{Kolmogorov Complexity; Algorithmic Information Theory; Simplicity; Abduction; Surprise}

% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
%\PACS{J0101}
%\MSC{}
%\JEL{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Diversity
%\LSID{\url{http://}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Applied Sciences:
%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Data:
%\dataset{DOI number or link to the deposited data set in cases where the data set is published or set to be published separately. If the data set is submitted and will be published as a supplement to this paper in the journal Data, this field will be filled by the editors of the journal. In this case, please make sure to submit the data set as a supplement when entering your manuscript into our manuscript editorial system.}

%\datasetlicense{license under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Toxins
%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Encyclopedia
%\encyclopediadef{Instead of the abstract}
%\entrylink{The Link to this entry published on the encyclopedia platform.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%The order of the section titles is: Introduction, Materials and Methods, Results, Discussion, Conclusions for these journals: aerospace,algorithms,antibodies,antioxidants,atmosphere,axioms,biomedicines,carbon,crystals,designs,diagnostics,environments,fermentation,fluids,forests,fractalfract,informatics,information,inventions,jfmk,jrfm,lubricants,neonatalscreening,neuroglia,particles,pharmaceutics,polymers,processes,technologies,viruses,vision

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}

\subsection{Theoretical Background}
\label{sec:theory}
Kolmogorov complexity formally quantifies the amount of information required
for the computation of a finite binary string\footnote{Though the definition
    holds for some infinite binary strings (think of the representation of the
    decimals of $\pi$), we restrict ourselves here to finite strings.} (or
any object represented by a finite binary
string)\cite{kolmogorov_three_1965,li_introduction_2008}. The complexity $K(s)$ of a (finite) binary string is the length in bits of the shortest program $p$
which, if given as input to a universal Turing Machine $U$, outputs $s$.
\begin{equation}
    \label{eq:kolmo_def}
    K_{U}(s) = \min_{p}\left\{l(p)|U(p)=s\right\}
\end{equation}

@@

\subsection{Computing the memorability of events}
\label{sec:computing}
\subsubsection{Retrieving an event}

@@

To model how humans are able to describe events by using qualifiers, we use \emph{predicates}: Boolean functions operating on events and, possibly, additional parameters: $\pi(e, a_1, a_2, \dots, a_n) \mapsto \{O,1\}$ is a predicate of arity $n$ operating on event $e$. In the rest of this paper, we will prefer the equivalent notation $\pi(e, k) \mapsto \{0,1\}$, where $k$ is a binary string encoding the sequence of arguments $a_1, \dots, a_n$. Using this notation, the predicate $\pi$ becomes a boolean function operating on $\mathbf{E} \times \{0,1\}^*$:
\begin{equation}
    \label{eq:predicate}
    \pi : \begin{cases}
        \mathcal{M}\times \{0,1\}^{*} & \mapsto \{0,1\}    \\
        (e, k)                        & \mapsto \pi_{k}(e)
    \end{cases}
\end{equation}
As an example of predicate, consider $\pi = \mathtt{year}$ and $k$ a string encoding the number $1$, thus
constructing the predicate $\mathtt{year(}e, 1\mathtt{)}$, which tells whether
the event $e$ occurred $1$ year ago.

@@

\subsubsection{Description complexity of events}

@@

\subsubsection{Computing Memorability}
As stated in Equation \ref{eq:memorability}, we define memorability $M(e)$ as the absolute difference between the description complexity of an event and its expected value. As we've just defined $K_d(e)$ and provided an approximation in Equation \ref{eq:approx_k_desc}, we now focus on defining the \emph{expected} description complexity of an event, $K_{exp}(e)$ that appears in Equation \ref{eq:memorability}

@@

\subsubsection{From memorability to abduction}
% On peut étendre la définition utilisée pour la surprise en faisant intervenir
% les prédicats'' `sympathiques` par rapport à ce que l'on questionne.
Abductive inference builds on the computation
of the memorability score. \emph{Knowing} that we want to find a cause $c$
for an observed effect $e$, we try to find the most remarkable event in past
memory that is related to $e$. While our ``memorability'' score identifies remarkable past events, it does not take into account their relatedness to $e$.

@@

This metrics answers the different problematics exposed in the introduction: by using a universal measure for complexity, bits, it allows to compare values from different dimensions. For instance, it solves the recency problem exposed above: is a big event a long time ago more memorable than a smaller one only a few minutes ago? The answer from conditional memorability is that "it depends". It depends on the complexity cost set for the predicates describing time and the magnitude of the event. These complexity costs should reflect the user's perception of the different dimensions (see Section \ref{sec:future}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

\subsection{Setup}

We design two different setups to test our approach. Both are inspired from smart home use cases.  This choice of
configuration is motivated by the challenges posed by smart homes for abductive
inference: i) as the number of connected devices increases, more events are
recorded, making the detection of memorable events more important; ii) smart
homes are prone to experience atypical situations, highly dependent on the context,
for which pre-established relations might fail to find good abduction
candidates. Our choice was also motivated by
the existence of previous work involving smart home simulations capable of quickly generating data from which we could extract events and test our methods.

\subsubsection{Scenario 1}
In this setup, we aim to reproduce the example mentioned in Section \ref{sec:introduction}: the installation of a brand new smart tv causes unpredicted effects on the light of a room.
To play this situation, we created a set of events covering a period of 100 days, corresponding to the past knowledge of the house. Two kinds of events are recorded: ``tv event'', corresponding to TV use, and luminosity events, describing the luminosity of the room at a given time. Low lights occur at night, and can occasionally occur during daytime, with a small probability. On the 100\textsuperscript{th} day, a ``tv event'' is recorded with a different ``device'' characteristic. Shortly after, the light lowers, which is recorded in the following ``light'' event.

\subsubsection{Scenario 2}
We considere here an experimental smart home setup, with various sensors, which we simulate over a period of time
To carry out the simulation, we built custom modules into the existing iCasa
smart home simulator\cite{lalanda_self-aware_2017}. ICasa
offers a simulation of autonomic systems that can handle internal communications,
the possible insertion of new components at runtime, or the deletion or modification of existing
components. We used a basic scenario consisting of a house with four rooms,
a single user, and an outdoor zone. All four rooms are equipped
with a temperature controller system that monitors and controls heaters (fig.
\ref{fig:view}).

@@

\subsection{Results}
\label{sec:example}
\subsubsection{Memorability}

@@

The ``memorability score'' is shown in Figure \ref{fig:result1}.
% highlights these aforementioned events from the main ``usual'' sequence. Since
the computation of this measure treats unusually complex or unusually simple events the
same way (from the absolute value operation in Equation \ref{eq:unexpected}), we
observe that some events are memorable due to their context only. For instance,
a temperature anomaly occurring simultaneously to many other anomalies is
noticeable, as it is costlier than expected to distinguish it from its neighbors.

@@

Given that we generated the data used for this experiment, it is possible to
flag all perturbation events from the usual daily events and evaluate how a
detection based on ``memorability'' score would perform in distinguishing these
events. The result is presented as a ROC curve in Figure \ref{fig:roc}.

\textbf{TODO:} Il faudrait commenter la courbe
\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth]{./figures/roc}
    \caption{Experimental ROC curve (True Positive Rate against False Positive
        Rate) for a classifier based on our memorability score. Measures consider 23
        manually flagged events as memorable (events added to the normal background
        as described in Section~\ref{sec:example}.)}
    \label{fig:roc}
\end{figure}
\subsubsection{Abduction}

To show the potential application to abductive inference, we use our approach to the first scenario, to see if memorabilty alone can find the brand new TV to be a reasonable cause for the sudden low light.

The result of our algorithm is given in Figure \ref{fig:abduction_res}. It shows that the system correctly identifies the TV as being the cause. The reason for this choice is that, since the tv's device ID is unique among all other events of type ``tv'', its description complexity is very low.

\begin{figure}
    \centering
    \includegraphics[width=.8\linewidth]{./figures/abduction_1_results}
    \caption{Outputs of the memorability-based abduction module. This represent the 3 events in the memory having the highest memorability score relative to the consequence event.}
    \label{fig:abduction_res}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}

\subsection{Related Works}
\label{sec:related}
\textbf{TODO: this section is still WIP: I've added most references and short comments, but I still need to write the story linking them.}
Our work is intended to be integrated into larger-scale frameworks to monitor
and detect events in complex environment such as smart homes. In these works, the
approach to smart homes is often regarded as self-organizing systems \cite{kramer_rigorous_2009,kounev_notion_2017}. As such, they present capacities of adaptation to new goals,
new components, new environment. A commonly used approach is the principle of
autonomic system, which minimizes user's intervention for management of the
system \cite{kounev_notion_2017,kephart_vision_2003}.

@@

\subsection{Perspectives}
\label{sec:future}
The main purpose of the present paper is to show the possible connections
between existing definitions of simplicity from cognitive science, Algorithmic
Information Theory and a practical use case in cyber-physical systems. As such,
many further improvements can be done to pave the way towards a better
integration and performance for anomaly detection or abduction.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
The introduction of description complexity and the subsequent memorability measure allows to compare events of various types with different characteristics. As such, it provides a framework to discriminate peculiar events and outliers.

The computation being based on predicates, the memorability score is entirely dependent on their definitions. This can be seen as a caveat or a feature of our approach: it makes the measure subjective while enabling the consideration of user's preferences in the definition and choice of predicates. This consideration can be the topic of future research and open up potential applications.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{6pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
%\supplementary{The following are available online at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title.}

% Only for the journal Methods and Protocols:
% If you wish to submit a video article, please do so with any other supplementary material.
% \supplementary{The following are available at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title. A supporting video article is available at doi: link.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{Conceptualization, É. Houzé and J-L. Dessalles; methodology, software, validation, writing--original draft, É. Houzé; supervision, writing--review and editing J-L. Dessalles, A. Diaconescu and D. Menga. All authors have read and aggreed to the submitted version of the manuscript.
}

\funding{\textbf{TODO je ne sais pas quoi mettre ici ? Indiquer le financement de la thèse ?}}

\dataavailability{All code and data used for the experiments can be found at \url{https://github.com/EtienneHouze/memorability_code}. The iCasa smart home simulator from the Adele research Group, which was used to generate sensor data, can be found at: \url{http://adeleresearchgroup.github.io/iCasa/snapshot/index.html}}

% \acknowledgments{In this section you can acknowledge any support given which is not covered by the author contribution or funding sections. This may include administrative and technical support, or donations in kind (e.g., materials used for experiments).}

\conflictsofinterest{The authors declare no conflict of interest.}

%% Optional
% \sampleavailability{Samples of the compounds ... are available from the authors.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Only for journal Encyclopedia
%\entrylink{The Link to this entry published on the encyclopedia platform.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional
% \abbreviations{Abbreviations}{
%     The following abbreviations are used in this manuscript:\\

%     \noindent
%     \begin{tabular}{@{}ll}
%         MDPI & Multidisciplinary Digital Publishing Institute \\
%         DOAJ & Directory of open access journals              \\
%         TLA  & Three letter acronym                           \\
%         LD   & Linear dichroism
%     \end{tabular}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional
% \appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
% \appendixstart
% \appendix
% \section{}
% \subsection{}
% The appendix is an optional section that can contain details and data supplemental to the main text---for example, explanations of experimental details that would disrupt the flow of the main text but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data are shown in the main text can be added here if brief, or as Supplementary Data. Mathematical proofs of results not central to the paper can be added as an appendix.

% \begin{specialtable}[H]
%     \small
%     \caption{This is a table caption. Tables should be placed in the main text near to the first time they are~cited.\label{tab2}}
%     \begin{tabular}{ccc}
%         \toprule
%         \textbf{Title 1} & \textbf{Title 2} & \textbf{Title 3} \\
%         \midrule
%         Entry 1          & Data             & Data             \\
%         Entry 2          & Data             & Data             \\
%         \bottomrule
%     \end{tabular}
% \end{specialtable}

% \section{}
% All appendix sections must be cited in the main text. In the appendices, Figures, Tables, etc. should be labeled, starting with ``A''---e.g., Figure A1, Figure A2, etc.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{paracol}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% To add notes in main text, please use \endnote{} and un-comment the codes below.
%\begin{adjustwidth}{-5.0cm}{0cm}
%\printendnotes[custom]
%\end{adjustwidth}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\reftitle{References}

% Please provide either the correct journal abbreviation (e.g. according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.

%=====================================
% References, variant A: external bibliography
%=====================================
\externalbibliography{yes}
\bibliography{biblio}
